---
title: "Tutorial 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library("gradethis")
library("learnr")
library("learnrhash")
library("tidyverse")
library("titanic")
knitr::opts_chunk$set(echo = FALSE)
```


# Bio 18 Learn R Tutorial 2

Be sure to click "Run Code" and "Submit Answer" where appropriate.  You may go back and fix code if an error is reported.

Let $X = \{1, 2, 3, ..., 99, 100\}$

## Sets

### Sequences

The provided code creates a sequence of natural numbers from 5 to 100 counting by multiples of 5. Create a sequence of natural numbers from 3 to 100 counting by multiples of 3.

```{r sequences, exercise = TRUE}
fives  <- seq(5, 100, 5)
print(fives)
threes <- seq(5, 100, 5)
```

```{r sequences-solution}
fives  <- seq(5, 100, 5)
print(fives)
threes <- seq(3, 100, 3)
```

```{r sequences-check}
grade_this_code()
```


### Intersection and Union

```{r union-setup}
fives  <- seq(5, 100, 5)
threes <- seq(3, 100, 3)
```


The provided code prints the intersection of fives and threes. Write another line of code that prints the union of fives and threes

```{r union, exercise = TRUE, exercise.lines = 2, exercise.setup = "union-setup"}
print(intersect(fives, threes))

```

```{r union-solution}
print(intersect(fives, threes))
print(union(fives, threes))
```

```{r union-check}
grade_this_code()
```

## Inclusion-Exclusion

### Cardinality

Print

* the `length` of `fives`
* the `length` of `threes`
* the `length` of the intersection of `fives` and `threes`
* the `length` of the union of `fives` and `threes`

```{r cardinality, exercise = TRUE, exercise.lines = 4, exercise.setup = "union-setup"}
print(length(fives))



```

```{r cardinality-solution}
print(length(fives))
print(length(threes))
print(length(intersect(fives, threes)))
print(length(union(fives, threes)))
```

```{r cardinality-check}
grade_this_code()
```


### Concept Check

Let $F$ be the event of randomly selecting from $X$ and getting a multiple of 5.

Let $T$ be the event of randomly selecting from $X$ and getting a multiple of 3.

Statement:

$$P(F \text{ or } T) = P(F) + P(T)$$

```{r concept-check-1}
quiz(
  question("Is the statement above TRUE or FALSE?",
    answer("TRUE"),
    answer("FALSE", correct = TRUE),
    allow_retry = TRUE
  )
)
```


## Conditional Probability

### Titanic Data

The `titanic` data set contains information about the famous Titanic shipwreck ([package documentation](https://www.kaggle.com/c/titanic/data)).  Here is a quick look at the `titanic_train` data.

```{r titanic-head}
head(titanic_train)
```

### Example of Data Mining

Here we compute the probability that a passenger was under 32 years old *given* that they were a first-class passenger.

```{r titanic-example, exercise = TRUE}
titanic_train %>%
  filter(Pclass == 1) %>%
  mutate(denominator = n()) %>%
  filter(Age < 32) %>%
  mutate(numerator = n()) %>%
  mutate(ratio = numerator / denominator) %>%
  summarize(cond_prob = unique(ratio))
```

## Conditional Probability Exercises

### Titanic Exercise 1

Compute the probability that a passenger was over 32 years old given that they were a third-class passenger.

```{r titanic-exercise-1, exercise = TRUE}

```

```{r titanic-exercise-1-solution}
titanic_train %>%
  filter(Pclass == 3) %>%
  mutate(denominator = n()) %>%
  filter(Age > 32) %>%
  mutate(numerator = n()) %>%
  mutate(ratio = numerator / denominator) %>%
  summarize(cond_prob = unique(ratio))
```

```{r titanic-exercise-1-check}
grade_this_code()
```

### Titanic Exercise 2

Compute the probability that a passenger was a third-class passenger *given* that they were over 32 years old.

```{r titanic-exercise-2, exercise = TRUE}

```

```{r titanic-exercise-2-solution}
titanic_train %>%
  filter(Age > 32) %>%
  mutate(denominator = n()) %>%
  filter(Pclass == 3) %>%
  mutate(numerator = n()) %>%
  mutate(ratio = numerator / denominator) %>%
  summarize(cond_prob = unique(ratio))
```

```{r titanic-exercise-2-check}
grade_this_code()
```

### Concept Check

$$P(A|B) = P(B|A)$$

```{r concept-check-2}
quiz(
  question("Is the statement above TRUE or FALSE?",
    answer("TRUE"),
    answer("FALSE", correct = TRUE),
    allow_retry = TRUE
  )
)
```

## Wrap Up

Type your name and UC Merced e-mail address inside the quotation marks

```{r student-info, exercise = TRUE}
student_name  <- ""
student_email <- ""
```


```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(
  ui_before = default_ui(url = "https://catcourses.ucmerced.edu")
)
```

