---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library("gradethis")
library("learnr")
library("learnrhash")
library("tidyverse")
library("visualize")
knitr::opts_chunk$set(echo = FALSE)
```

# Bio 18 LearnR Tutorial 4

Today, you are picking an avocado for dinner tonight.  In the bin, suppose that there is a 32 percent chance of randomly selecting a ripe avocado.  If you buy a bag of avocados, you do not inspect the fruit until you get home and inspect the bag of avocados all at once.

## Bin(n,p)

For the following calculations, use the `dbinom` or `pbinom` commands (maybe along with other R functions that have been introduced).

### Exactly

What is the probability that you have exactly 3 ripe avocados in a bag of 7 avocados?

```{r q2, exercise = TRUE, exercise.lines = 1}

```

```{r q2-check}
grade_this({
  if (abs(.result - dbinom(3, 7, 0.32) ) < 0.001){
    pass()
  }
  fail()
})
```


### Fewer

What is the probability that you have fewer than 4 ripe avocados among a bag of 8 avocados?

```{r q3, exercise = TRUE, exercise.lines = 1}

```

```{r q3-check}
grade_this({
  if (abs(.result - sum(dbinom(0:4, 8, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```


### More

What is the probability that you have more than 3 ripe avocados in your bag of 6 avocados?

```{r q6, exercise = TRUE, exercise.lines = 1}

```

```{r q6-check}
grade_this({
  if (abs(.result - sum(dbinom(4:6, 6, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```


## Inclusive Inequalities

In mathematics, the *strict* inequalities are "less than" ($<$) and "greater than" ($>$); while the *inclusive* inequalities are "less than or equal" ($\leq$) and "greater than or equal" ($\geq$).

### At Least

What is the probability that you have at least 4 ripe avocados in your bag of 7 avocados?

```{r q7, exercise = TRUE, exercise.lines = 1}

```

```{r q7-check}
grade_this({
  if (abs(.result - sum(dbinom(4:7, 7, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```


### At Most

What is the probability that you have at most 5 ripe avocados from the your bag of 9 avocados?

```{r q10, exercise = TRUE, exercise.lines = 1}

```

```{r q10-check}
grade_this({
  if (abs(.result - sum(dbinom(0:5, 9, 0.32)) ) < 0.001){
    pass()
  }
  fail()
})
```

## Visualize

Here are some examples of using the `visualize` package (created by Dr. Balamuta at UIUC)

```{r binom-at-most, exercise = TRUE, exercise.lines = 2}
visualize.binom(stat = 3, size = 5, prob = 0.32, section = "lower", strict = FALSE)
```

```{r binom-more, exercise = TRUE, exercise.lines = 2}
visualize.binom(stat = 3, size = 5, prob = 0.32, section = "upper", strict = TRUE)
```

```{r geom-less, exercise = TRUE, exercise.lines = 2}
visualize.binom(stat = 3, prob = 0.32, section = "lower", strict = TRUE)
```

```{r geom-at-least, exercise = TRUE, exercise.lines = 2}
visualize.binom(stat = 3, prob = 0.32, section = "upper", strict = FALSE)
```

## Binomial CMF

On this page, $X \sim \text{Bin}(6, 0.32)$

Use the `visualize.binom` function to create the graph of $P(k < 4)$

```{r q11, exercise = TRUE, exercise.lines = 2}

```

```{r q11-solution}
visualize.binom(stat = 4, size = 6, prob = 0.32, section = "lower", strict = TRUE)
```

```{r q11-check}
grade_this_code()
```

Use the `visualize.binom` function to create the graph of $P(k \geq 2)$

```{r q12, exercise = TRUE, exercise.lines = 2}

```

```{r q12-solution}
visualize.binom(stat = 2, size = 6, prob = 0.32, section = "upper", strict = FALSE)
```

```{r q12-check}
grade_this_code()
```


## Wrap Up

Type your name and UC Merced e-mail address inside the quotation marks

```{r student-info, exercise = TRUE}
student_name  <- ""
student_email <- ""
```


```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(
  ui_before = default_ui(url = "https://catcourses.ucmerced.edu")
)
```


