---
title: "Tutorial 3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library("gradethis")
library("learnr")
library("learnrhash")
library("tidyverse")
library("titanic")
knitr::opts_chunk$set(echo = FALSE)
```


# Bio 18 Learn R Tutorial 3

Be sure to click "Run Code" and "Submit Answer" where appropriate.  You may go back and fix code if an error is reported.



## Bayes Rule 1

### Concept Check

$$P(A|B) = P(B|A)$$

```{r concept-check-1}
quiz(
  question("Is the statement above TRUE or FALSE?",
    answer("TRUE"),
    answer("FALSE", correct = TRUE),
    allow_retry = TRUE
  )
)
```

### Example 1



A 2009 federal study showed that 63.8% of occupants involved in a fatal car crash wore seat belts.  Of those in a fatal crash who wore seat belts, 2% were ejected from the vehicle.  For those not wearing seat belts, 36% were ejected from the vehicle.  (Source:  National Highway Traffic Safety Administration)

Let

* E: passenger was ejected from the vehicle
* S: passenger was wearing a seat belt

```{r seatbelts1}
quiz(
  question("Translate the following into math notation: 'A 2009 federal study showed that 63.8 percent of occupants involved in a fatal car crash wore seat belts.'",
    answer("P(S) = 0.638", correct = TRUE),
    answer("P(S|E) = 0.638"),
    answer("P(E|S) = 0.638"),
    answer("P(E|S^c ) = 0.638"),
    answer("P(S|E^c ) = 0.638"),
    allow_retry = TRUE,
    random_answer_order = TRUE
  )
)
```

```{r seatbelts2}
quiz(
  question("Translate the following into math notation: 'For those not wearing seat belts, 36% were ejected from the vehicle.'",
    answer("P(S) = 0.36"),
    answer("P(S|E) = 0.36"),
    answer("P(E|S) = 0.36"),
    answer("P(E|S^c ) = 0.36", correct = TRUE),
    answer("P(S|E^c ) = 0.36"),
    allow_retry = TRUE,
    random_answer_order = TRUE
  )
)
```

```{r seatbelts3}
quiz(
  question("Translate the following into math notation: 'Of those in a fatal crash who wore seat belts, 2% were ejected from the vehicle.'",
    answer("P(S) = 0.02"),
    answer("P(S|E) = 0.02"),
    answer("P(E|S) = 0.02", correct = TRUE),
    answer("P(E|S^c ) = 0.02"),
    answer("P(S|E^c ) = 0.02"),
    allow_retry = TRUE,
    random_answer_order = TRUE
  )
)
```

Given that the passenger in a fatal car crash was ejected from the vehicle, find the probability that that passenger was wearing a seat belt.

```{r seatbelts4, exercise = TRUE}
answer1 <- 0.1234 #replace this number with the correct answer
answer1 #leave this line of code as is for the grader
```

```{r, seatbelts4-check}
grade_this({
  if (abs(.result - 0.0892 ) < 0.001){
    pass()
  }
  fail()
})
```


## Bayes Rule 2

### Example 2

Suppose that, for a fictional country, the probability that a missing airplane is discovered is given by

$$P(D) = 0.7$$

Furthermore, we are handed studies which show that

$$P(L|D) = 0.6$$
$$P(L^{c}|D^{c}) = 0.9$$

where $L$ is the event that the airplane had an emergency locator.

```{r airplane1}
quiz(
  question(sprintf("Interpret $P(L|D)$"),
    answer("the probability that the airplane has an emergency locator given that it was discovered", correct = TRUE),
    answer("the probability that the airplane has an emergency locator given that it was not discovered"),
    answer("the probability that the airplane has an emergency locator and that it was discovered"),
    answer("the probability that the airplane has an emergency locator and that it was not discovered"),
    allow_retry = TRUE,
    random_answer_order = TRUE
  )
)
```

```{r airplane2}
quiz(
  question(sprintf("Interpret $P( L^c | D^c ) = 0.90$"),
    answer("the probability that an airplane does not have an emergency locator given that it was not discovered is 90%", correct = TRUE),
    answer("the probability that an airplane does not have an emergency locator given that it was discovered is 90%"),
    answer("the probability that an airplane does have an emergency locator given that it was discovered is 90%"),
    answer("the probability that an airplane does have an emergency locator given that it was not discovered is 90%"),
    allow_retry = TRUE,
    random_answer_order = TRUE
  )
)
```

Compute $P(D^{c}|L)$

```{r airplane3, exercise = TRUE}
answer2 <- 0.1234 #replace this number with the correct answer
answer2 #leave this line of code as is for the grader
```

```{r, airplane3-check}
grade_this({
  if (abs(.result - 0.0667 ) < 0.001){
    pass()
  }
  fail()
})
```


## Discrete Probability Distribution

```{r banana1, exercise = TRUE}
# https://www.amazon.com/Hutzler-3571-571-Banana-Slicer/dp/B0047E0EII/
stars <- 1:5
probs <- c(4, 4, 8, 12, 72) / 100

df <- data.frame(stars, probs)

df %>%
  ggplot(aes(x = stars, y = probs)) +
  geom_bar(fill = "seagreen3", stat = "identity") +
  labs(title = "Banana Slicer",
       subtitle = "Amazon ratings",
       caption = "Bio 18",
       x = "stars",
       y = "probability") +
  theme_minimal()
```

```{r banana2}
quiz(
  question("This graph is a ",
    answer("bar plot", correct = TRUE),
    answer("histogram"),
    answer("scatterplot"),
    answer("line plot"),
    allow_retry = TRUE,
    random_answer_order = TRUE
  )
)
```

```{r banana3}
quiz(
  question("Which of the following descriptions is most appropriate for the graph?",
    answer("skewed left", correct = TRUE),
    answer("skewed right"),
    answer("bell curve"),
    allow_retry = TRUE,
    random_answer_order = TRUE
  )
)
```

What is the probability that a user rated the item either "4" or "5"?  Please input your answer as a decimal number.

```{r banana4, exercise = TRUE}
answer3 <- 0.18 #replace this number with the correct answer
answer3 #leave this line of code as is for the grader
```

```{r, banana4-check}
grade_this({
  if (abs(.result - 0.84) < 0.01){
    pass()
  }
  fail()
})
```



## Wrap Up

Type your name and UC Merced e-mail address inside the quotation marks

```{r student-info, exercise = TRUE}
student_name  <- ""
student_email <- ""
```


```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(
  ui_before = default_ui(url = "https://catcourses.ucmerced.edu")
)
```

