---
title: "LearnR Homework 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
# library("gradethis")
library("learnr")
library("tidyverse")
knitr::opts_chunk$set(echo = FALSE)
# gradethis::gradethis_setup()
num_correct <- 0
```

# LearnR Homework

This `LearnR` setting lets the teacher make self-paced tutorials that ease instruction of R programming.

## Setup

First, please enter your full name and UC Merced e-mail address into the variables below.  Be sure to keep the strings inside of the quotation marks.  Press `Run Code` to verify the input.

```{r name_field, exercise = TRUE}
student_name  <- ""
student_email <- ""
print(student_name)
print(student_email)
```

```{r name_field-check, exercise.setup = "name_field"}
# grade_result(
#   pass_if(is.character(student_name) & length(student_name) > 0 &
#             is.character(student_email) & length(student_email) > 13)
# )
if(is.character(student_name) & 
   length(student_name) > 0 &
   is.character(student_email) & 
   length(student_email) > 13){
     num_correct <- num_correct + 1
   }
```

## Arrays

In `R`, we use the `c()` function to concatenate data (such as numbers or strings) into arrays.

```{r universal_set, exercise = TRUE}
universal_set <- seq(1,32)
print(universal_set)
```

For instance, the following code creates an array that contains the multiples of 5 between 1 and 32.

```{r fives, exercise = TRUE, exercise.lines = 1}
fives <- c(5, 10, 15, 20, 25, 30)
```

Create an array called `threes` that contains the multiples of 3 between 1 and 32.

```{r threes, exercise = TRUE, exercise.lines = 2}
threes <- c()
```

```{r threes-check, exercise.setup = "threes"}
# grade_result(pass_if(length(.result) == 10))
if(length(threes) == 10){
  num_correct <- num_correct + 1
}
```

## Intersection and Union

```{r sets_setup}
fives  <- seq(5, 30, 5)
threes <- seq(3, 30, 3)
```

Recall that the *intersection* of two sets has the elements that appear in both sets, while the *union* of two sets has the elements that appear in at least one set.  Here is how we can compute the `intersect` of `fives` and `threes` in R.

```{r intersect_example, exercise = TRUE, exercise.lines = 1, exercise.setup = "sets_setup"}
intersect(fives, threes)
```

Compute the `union` of `fives` and `threes` in the code block below (after the assignment arrow).

```{r union_exercise, exercise = TRUE, exercise.lines = 1, exercise.setup = "sets_setup"}
union_of_fives_and_threes <- 1337
```

```{r union_excerise-check, exercise.setup = "union_exercise"}
# grade_result(pass_if(length(.result) == 14))
if(length(.result) == 14){
  num_correct <- num_correct + 1
}
```

